Improving content discovery through combining linked data and data mining techniques

### 2016-05-06 report/chapters/01-intro.tex
Bit more for chapter 2
Spell check

\chapter{Introduction}

@@

Technologies such as the World Wide Web and the maturity of the
media industry in its adoption in the last decade creates both an
opportunity to give consumers access to a substantial amount of
media content and a challenge in trying to make cohesive sense of
a diverse range of content, perhaps produced in an organistion that
was traditionally very fragmented as the BBC was.

@@

\item Research and software tools around the concept of
  \emph{Linked Data} can aid us in rapidly acquiring a broad view
  (perhaps initially at the expense of depth) of a organisation's
  content whilst also providing a platform for simple enrichment of
  that content's metadata.

@@

\item Linked Data and Semantic Web \emph{ontologies} and models
  available can provide data enrichment beyond attributes and keywords
  explicitly avaiable within content data or metadata.

>>>>

\chapter{Introduction}
\label{chp:intro}

@@

Technologies such as the World Wide Web and the maturity of the
media industry in its adoption in the last decade creates both an
opportunity to give consumers access to a substantial amount of
media content and a challenge in trying to make cohesive sense of
a diverse range of content, perhaps produced in an organisation that
was traditionally very fragmented as the BBC was.

@@

\item Research and software tools around the concept of
  \emph{Linked Data} can aid us in rapidly acquiring a broad view
  (perhaps initially at the expense of depth) of a organisation's
  content while also providing a platform for simple enrichment of
  that content's metadata.

@@

\item Linked Data and Semantic Web \emph{ontologies} and models
  available can provide data enrichment beyond attributes and keywords
  explicitly available within content data or metadata.

### 2016-05-06 report/chapters/02-background.tex
Spell check

Well-known examples include neural networks, decision trees and or
linear regression. In all supervised learning techniques, we can
normally assess the model's performance against traning data for
which we already know the answers. We can see supervised learning
thus as a computational attempt to extrapolate human knowledge into
a reusable model that can predict or determine things at a speed
and scale humans would not normally be able to work through manually
(e.g. predicting weather with manual calculations or diagnosing
patients more quickly and with greater accuracy).

@@

A well-known example is association rule mining that can find
interesting relations in data sets that were perhaps previously
unknwown. A classic implementation of this technique is in
supermarkets and other commercial enterprises where those
organisations seek to find rules and patterns in consumer purchasing
habits so that they can try to promote items that customers might
want to buy based on other items they are currently trying to
purchase.

@@

Another major unsupervised learning technique -- and the focus of
this research -- is \emph{clustering}. In clustering algoriths, we
seek to group similar items or entities together in groups or
\emph{clusters}. Clustering has many applications, but in this
work the focus will be around \emph{hierarchical} clustering which
is effective for grouping together items that appear to be
connected in some way -- in our case that the media content is
connected by virtue of a common theme, topic or genre.

@@

Hierchical clustering differs from, say,
\emph{k-means clustering}\cite{witten2005data} in that
we start with no assumption about the number of clusters or groups
the data will be divided into. This method is generally applied
\emph{agglomeratively} or \emph{divisively}.

In divisive, hierarchical clustering, we start with all elements in
a single cluster and proceed to find divisons that best split that
cluster. This is applied recursively until we generate a
dendrogam\cite{witten2005data} showing a full hierarchy of similarity
between the items or we can halt the division based on some condition,
e.g. only split clusters with a low cohesion below some threshold
and stop on the first attempt to split a cohesive cluster above
that threshold.

Agglomerative, hierarchical clustering goes in the opposite direction
by starting with all items in their own, individual clusters.
The two ``nearest'' clusters are then recursively merged until, again,
we have a full dendrogam or stop before we are about to create a
cluster whose cohesion falls below some threshold.

@@

In this experiment, Jaccard distance\cite{witten2005data}
based on its suitability for binary, asymmetric data. It is argued
that the vast vocabularly offered by all potential semantic web
RDF triples will lead to very asymmetric binary values based on the
presence or non-presence of that triple.

The chosen linkage function was the complete linkage
on the basis that it ensures that any two content items
within a cluster to be considered related. This avoids the so-called
\emph{chaining phenomenum} where single linkage may create clusters
where two unrelated items are members because they are each related
to an item of chain of related items
therebetween.\cite{everitt2011hierarchical}

@@

In this section, the goal is to strengthen that case and review other
previous work around using linked data in the enterprise. This is a more
general argument for any enterprise with data (e.g. internal information
about staff or business processes) and not just media orgainisations.

@@

It is rare, however, for any large business to keep all data stored in
one location and in one format. Even fairly simple businesses will have
separate data stores for their employee data, for example, and all
usernames and passwords for the corporate email system. Without much effort,
a business that implements or purchases two distinct systems for personnel
and email has already fragmented its data.

There may be no difficulty from this initially, but then a problem arises
where it is noted that employees, in this example, do not automatically have
their email accounts disabled when they leave the organisation. Smaller
businesses might simple employ adminstrative staff to keep databases in
sync and implement a standard process to handle the case of an employee
leaving the company.

@@

In a media organisation, it might be argued that whilst all employee and
internal systems data is in bespoke systems, we can ensure all ``content''
is stored in a single system such as a \emph{content management system}. This
can be strained by at least three different pressures:

@@

Hohpe and Woolf\cite{hohpe2002enterprise} described a comprehensive
set of software design and architecture patterns that apply to this
field, but almost every pattern implies creating bespoke data flow
sofware for any given integration.

>>>>

Well-known examples include neural networks, decision trees and or
linear regression. In all supervised learning techniques, we can
normally assess the model's performance against training data for
which we already know the answers. We can see supervised learning
thus as a computational attempt to extrapolate human knowledge into
a reusable model that can predict or determine things at a speed
and scale humans would not normally be able to work through manually
(e.g. predicting weather with manual calculations or diagnosing
patients more quickly and with greater accuracy).

@@

A well-known example is association rule mining that can find
interesting relations in data sets that were perhaps previously
unknown. A classic implementation of this technique is in
supermarkets and other commercial enterprises where those
organisations seek to find rules and patterns in consumer purchasing
habits so that they can try to promote items that customers might
want to buy based on other items they are currently trying to
purchase.

@@

Another major unsupervised learning technique -- and the focus of
this research -- is \emph{clustering}. In clustering algorithm, we
seek to group similar items or entities together in groups or
\emph{clusters}. Clustering has many applications, but in this
work the focus will be around \emph{hierarchical} clustering which
is effective for grouping together items that appear to be
connected in some way -- in our case that the media content is
connected by virtue of a common theme, topic or genre.

@@

Hierarchical clustering differs from, say,
\emph{k-means clustering}\cite{witten2005data} in that
we start with no assumption about the number of clusters or groups
the data will be divided into. This method is generally applied
\emph{agglomeratively} or \emph{divisively}.

In divisive, hierarchical clustering, we start with all elements in
a single cluster and proceed to find divisions that best split that
cluster. This is applied recursively until we generate a
dendrogram\cite{witten2005data} showing a full hierarchy of similarity
between the items or we can halt the division based on some condition,
e.g. only split clusters with a low cohesion below some threshold
and stop on the first attempt to split a cohesive cluster above
that threshold.

Agglomerative, hierarchical clustering goes in the opposite direction
by starting with all items in their own, individual clusters.
The two ``nearest'' clusters are then recursively merged until, again,
we have a full dendrogram or stop before we are about to create a
cluster whose cohesion falls below some threshold.

@@

In this experiment, Jaccard distance\cite{witten2005data}
based on its suitability for binary, asymmetric data. It is argued
that the vast vocabulary offered by all potential semantic web
RDF triples will lead to very asymmetric binary values based on the
presence or non-presence of that triple.

The chosen linkage function was the complete linkage
on the basis that it ensures that any two content items
within a cluster to be considered related. This avoids the so-called
\emph{chaining phenomenon} where single linkage may create clusters
where two unrelated items are members because they are each related
to an item of chain of related items
therebetween.\cite{everitt2011hierarchical}

@@

In this section, the goal is to strengthen that case and review other
previous work around using linked data in the enterprise. This is a more
general argument for any enterprise with data (e.g. internal information
about staff or business processes) and not just media organisations.

@@

It is rare, however, for any large business to keep all data stored in
one location and in one format. Even fairly simple businesses will have
separate data stores for their employee data, for example, and all
user names and passwords for the corporate email system. Without much effort,
a business that implements or purchases two distinct systems for personnel
and email has already fragmented its data.

There may be no difficulty from this initially, but then a problem arises
where it is noted that employees, in this example, do not automatically have
their email accounts disabled when they leave the organisation. Smaller
businesses might simple employ administrative staff to keep databases in
sync and implement a standard process to handle the case of an employee
leaving the company.

@@

In a media organisation, it might be argued that while all employee and
internal systems data is in bespoke systems, we can ensure all ``content''
is stored in a single system such as a \emph{content management system}. This
can be strained by at least three different pressures:

@@

Hohpe and Woolf\cite{hohpe2002enterprise} described a comprehensive
set of software design and architecture patterns that apply to this
field, but almost every pattern implies creating bespoke data flow
software for any given integration.

### 2016-05-06 report/chapters/03-design.tex
Spell check

The content miner breaks down into two general components: a pipeline
that prepares the data for machine learning and the clustering at the
end on that prepared data. The primary focus of this work is to
evaluate approaches for the former in the form of a
\emph{data pipeline} that uses semantics to take in a content item's
identifer at the source end and produces feature sets for data mining
at the output end. This data pipeline is inductively defined and
designed in the following section.

@@

As stated in the previous sectionh, a core subsystem in the overall
system is a conceptual data pipeline whose input is a URI or IRI
identifying a content item published on an organisation's website and
the output is feature sets ready for applying machine learning.

@@

In Chapter~\ref{chp:implementation}, aa system is engineered that implements
as many of these pipeline stages as possible such that a running instance of
the application can configure which components to use and which not to use.
Then in Chapter~\ref{chp:evaluation}, an evalution of the system is given
while it is running each component in isolation to demonstrate which of the
theoretically-defined processes in this chapter appears to be most effective
in generating feature sets specifically for clustering web content.

@@

Note that Figure~\ref{fig:gen-null} shows all three data structures involved
despite having no functional use. We can also see top-level definitions of the
process where we first \emph{extract} semantic information in RDF from a
content item indentified by IRI and then \emph{generate} features therefrom.
More useful models can now be inductively defined by adding atomic
subcomponents that may each add value to the overall transformation.

@@

        IRI -> RDFa [label="derefernce"];
        RDFa -> RDF [label="parse"];
        RDF -> Features [label="(IRI)"];
      }
    \end{dot2tex}
  \end{center}
  \caption{Semantic web data extraction\label{fig:gen-rdfa}}
\end{figure}

@@

As also noted by Paulheim
and F\"urnkranz, this overlooks the
\emph{open world assumption}\cite{russel2010artificial}. However, application
of clustering algorithms on binary data can employ asymmetric distance metrics
such as Jaccard similarity coeffcient\cite{witten2005data}, which notably
avoids deriving similarity from negative values. That is, two content items
lacking a particular property will contribute no information about their
(dis)similarity. Thus we safely avoid inadvertently grouping together one item
that genuinely lacks the property with another that indeed has the property,
but we lack the positive assertion thereof in the data extracted.

@@

The basic pipeline in Figure~\ref{fig:gen-rdfa} can thus be augmented with this
basic feature extraction to produce the pipeline depicated in
Figure~\ref{fig:gen-rdfa-basic}.

@@

The third and final direction in which this data pipeline can be improved is
in terms of data enrichment. A simple strategy here is to repeat the
deferencing used in Section~\ref{sec:rdf-extraction}, but for each IRI
found as the object of a triple in which the initial IRI is the subject.
Formally:

@@

        IRI -> RDFa [label="dereference"];
        RDFa -> RDF [label="parse"];
        RDF -> RDF1 [label="dereference/parse"];
        RDF -> RDF2 [label="dereference/parse"];
        RDF -> RDFp [label="\cup"];
        RDF1 -> RDFp [label="\cup"];
        RDF2 -> RDFp [label="\cup"];
        RDFp -> Features [label="content\_?p\_?v"];
      }
    \end{dot2tex}
  \end{center}
  \caption{\label{fig:object.-deref}Semantic web content miner with addtional dereferencing of linked entities}
\end{sidewaysfigure}

@@

        IRI -> RDFa [label="derefernce"];
        IRI -> Text [label="GET"];
        RDFa -> RDF1 [label="parse"];
        Text -> RDF2 [label="entity extraction"];
        RDF1 -> RDF [label="\cup"];
        RDF2 -> RDF [label="\cup"];
        RDF -> Features [label="content\_?p\_?v"];
      }
    \end{dot2tex}
  \end{center}
  \caption{Named entity extraction in addition to semantic web extraction\label{fig:entity-extraction}}
\end{sidewaysfigure}

@@

\noindent might prove -- through experiementation -- to be useful enough
for data mining insights.

The fourth and final extraction strategy explored is acquiring metadata from
bespoke Content Management Systems and other internal APIs. This is generally
the only option used in enterprises settings, as discussed in
Section~\ref{sec:linked-enterprise-data}. This is likely to be the richest
source of information where an enterprise has typically preferred bespoke
integrations against non-hypermedia interfaces, so experimentation should
help quantity or qualify the value such a direct integration adds (perhaps to
consider it in combination with the cost of bepsoke, repeated integration
projects).

@@

\begin{itemize}
\item inferring relationships to hypernyms as defined by Wordnet\cite{miller1995wordnet};
\item inferring facts based using rules derirved from expert domain knowledge;
\item using RDFS and OWL to generate new triples with well-established Ontology rules.
\end{itemize}

@@

\noindent might be useful ot help cluster articles that take place in the same
country -- even if the countries are not always explicitly mentioned therein.
Such an inference requires knowledge about cities and countries to
write and domain experts for different types of content might be able to offer
more nuanced rules.

@@

In this section, a data pipeline was inductively built up from a base,
identify pipeline with suggestions for potential improvements in different
stages. An application of all the ideas discussed so far might look like
that depicated in Figure~\ref{fig:maximal-pipeline}.

>>>>

The content miner breaks down into two general components: a pipeline
that prepares the data for machine learning and the clustering at the
end on that prepared data. The primary focus of this work is to
evaluate approaches for the former in the form of a
\emph{data pipeline} that uses semantics to take in a content item's
identifier at the source end and produces feature sets for data mining
at the output end. This data pipeline is inductively defined and
designed in the following section.

@@

As stated in the previous section, a core subsystem in the overall
system is a conceptual data pipeline whose input is a URI or IRI
identifying a content item published on an organisation's website and
the output is feature sets ready for applying machine learning.

@@

In Chapter~\ref{chp:implementation}, a system is engineered that implements
as many of these pipeline stages as possible such that a running instance of
the application can configure which components to use and which not to use.
Then in Chapter~\ref{chp:evaluation}, an evaluation of the system is given
while it is running each component in isolation to demonstrate which of the
theoretically-defined processes in this chapter appears to be most effective
in generating feature sets specifically for clustering web content.

@@

Note that Figure~\ref{fig:gen-null} shows all three data structures involved
despite having no functional use. We can also see top-level definitions of the
process where we first \emph{extract} semantic information in RDF from a
content item identified by IRI and then \emph{generate} features therefrom.
More useful models can now be inductively defined by adding atomic
subcomponents that may each add value to the overall transformation.

@@

        IRI -> RDFa [label="dereference"];
        RDFa -> RDF [label="parse"];
        RDF -> Features [label="(IRI)"];
      }
    \end{dot2tex}
  \end{center}
  \caption{Semantic web data extraction\label{fig:gen-rdfa}}
\end{figure}

@@

As also noted by Paulheim
and F\"urnkranz, this overlooks the
\emph{open world assumption}\cite{russel2010artificial}. However, application
of clustering algorithms on binary data can employ asymmetric distance metrics
such as Jaccard similarity coefficient\cite{witten2005data}, which notably
avoids deriving similarity from negative values. That is, two content items
lacking a particular property will contribute no information about their
(dis)similarity. Thus we safely avoid inadvertently grouping together one item
that genuinely lacks the property with another that indeed has the property,
but we lack the positive assertion thereof in the data extracted.

@@

The basic pipeline in Figure~\ref{fig:gen-rdfa} can thus be augmented with this
basic feature extraction to produce the pipeline depicted in
Figure~\ref{fig:gen-rdfa-basic}.

@@

The third and final direction in which this data pipeline can be improved is
in terms of data enrichment. A simple strategy here is to repeat the
dereferencing used in Section~\ref{sec:rdf-extraction}, but for each IRI
found as the object of a triple in which the initial IRI is the subject.
Formally:

@@

        IRI -> RDFa [label="dereference"];
        RDFa -> RDF [label="parse"];
        RDF -> RDF1 [label="dereference/parse"];
        RDF -> RDF2 [label="dereference/parse"];
        RDF -> RDFp [label="\cup"];
        RDF1 -> RDFp [label="\cup"];
        RDF2 -> RDFp [label="\cup"];
        RDFp -> Features [label="content\_?p\_?v"];
      }
    \end{dot2tex}
  \end{center}
  \caption{\label{fig:object.-deref}Semantic web content miner with additional dereferencing of linked entities}
\end{sidewaysfigure}

@@

        IRI -> RDFa [label="dereference"];
        IRI -> Text [label="GET"];
        RDFa -> RDF1 [label="parse"];
        Text -> RDF2 [label="entity extraction"];
        RDF1 -> RDF [label="\cup"];
        RDF2 -> RDF [label="\cup"];
        RDF -> Features [label="content\_?p\_?v"];
      }
    \end{dot2tex}
  \end{center}
  \caption{Named entity extraction in addition to semantic web extraction\label{fig:entity-extraction}}
\end{sidewaysfigure}

@@

\noindent might prove -- through experimentation -- to be useful enough
for data mining insights.

The fourth and final extraction strategy explored is acquiring metadata from
bespoke Content Management Systems and other internal APIs. This is generally
the only option used in enterprises settings, as discussed in
Section~\ref{sec:linked-enterprise-data}. This is likely to be the richest
source of information where an enterprise has typically preferred bespoke
integrations against non-hypermedia interfaces, so experimentation should
help quantity or qualify the value such a direct integration adds (perhaps to
consider it in combination with the cost of bespoke, repeated integration
projects).

@@

\begin{itemize}
\item inferring relationships to hypernyms as defined by Wordnet\cite{miller1995wordnet};
\item inferring facts based using rules derived from expert domain knowledge;
\item using RDFS and OWL to generate new triples with well-established Ontology rules.
\end{itemize}

@@

\noindent might be useful to help cluster articles that take place in the same
country -- even if the countries are not always explicitly mentioned therein.
Such an inference requires knowledge about cities and countries to
write and domain experts for different types of content might be able to offer
more nuanced rules.

@@

In this section, a data pipeline was inductively built up from a base,
identify pipeline with suggestions for potential improvements in different
stages. An application of all the ideas discussed so far might look like
that depicted in Figure~\ref{fig:maximal-pipeline}.

### 2016-05-06 report/chapters/04-implementation.tex
Spell check

That is, whilst the different strategies illustrated in the maximal
data pipline in Figure~\ref{fig:maximal-pipeline} can be run in
parallel, the extraction stage itself simply converts the identity
graph described in section~\ref{sec:identity-graph} to a single graph
(after having taken the union of all the strategies).

@@

    # Empty set removed from powerset
    for idx, gs in enumerate(powerset(graphs) - {{},}):
        # union defined elsewhere: list(graph) -> graph
        graph = reduce(union, gs)
        # Loop counter idx tells us from which technique
        # combination each graph comes
        yield idx, graph
  \end{lstlisting}
\end{centering}

An illustrative Python function is shown in
Listings~\ref{lst:extract-all} where each of the three extraction
techniques is invoked only once and a powerset function is used to
generate all possible unions of those graphs and thus yield all
possible usages or non-usages of each strategy to generate RDF
graphs. The details of the three extraction functions are covered in
section~\ref{impl-extraction}.

@@

As introduced in section~\ref{intro-problems}, all that content is
also likely to be distributed across multiple databases, content
management systems and other stores. Whilst it is hypothesised in
this research that semantics and linked data provide a good way to
extract data about the total breadth of all content without any
bespoke integration against internal systems, there still remains
the enterprise integration problem of \emph{discovery} of those
content items.

@@

Another feature in listings~\ref{lst:find-links} is a restriction
to consider only links to other BBC pages. There may be a positive
or negative effect in addtionally noting external pages linked to from
content pages, but that is left to future research to consider.

@@

\begin{centering}
  \begin{lstlisting}[
      label=lst:enrich,
      language=python,
      caption={Python function that enriches a graph via deferencing objects}]
import rfc3987

@@

The feature generation strategy employed was dervied from a distilled
portion of the approach introduced by Paulheim
and F\"urnkranz\cite{paulheim2012unsupervised}.

@@

For each approach, hiearchical clustering was applied repeatedly
until the next merge would produce a cluster with cohesion below 0.5.
This is reasonably arbitrary as each technique will have different
concepts of cohesion, but it provided a strong basis on which to
evaluate each approach on whether its cohesion meaningfully predicts
whether a human would agree that cluster contains related items.

>>>>

That is, while the different strategies illustrated in the maximal
data pipeline in Figure~\ref{fig:maximal-pipeline} can be run in
parallel, the extraction stage itself simply converts the identity
graph described in section~\ref{sec:identity-graph} to a single graph
(after having taken the union of all the strategies).

@@

    # Empty set removed from power set
    for idx, gs in enumerate(powerset(graphs) - {{},}):
        # union defined elsewhere: list(graph) -> graph
        graph = reduce(union, gs)
        # Loop counter idx tells us from which technique
        # combination each graph comes
        yield idx, graph
  \end{lstlisting}
\end{centering}

An illustrative Python function is shown in
Listings~\ref{lst:extract-all} where each of the three extraction
techniques is invoked only once and a power set function is used to
generate all possible unions of those graphs and thus yield all
possible usages or non-usages of each strategy to generate RDF
graphs. The details of the three extraction functions are covered in
section~\ref{impl-extraction}.

@@

As introduced in section~\ref{intro-problems}, all that content is
also likely to be distributed across multiple databases, content
management systems and other stores. While it is hypothesised in
this research that semantics and linked data provide a good way to
extract data about the total breadth of all content without any
bespoke integration against internal systems, there still remains
the enterprise integration problem of \emph{discovery} of those
content items.

@@

Another feature in listings~\ref{lst:find-links} is a restriction
to consider only links to other BBC pages. There may be a positive
or negative effect in additionally noting external pages linked to from
content pages, but that is left to future research to consider.

@@

\begin{centering}
  \begin{lstlisting}[
      label=lst:enrich,
      language=python,
      caption={Python function that enriches a graph via dereferencing objects}]
import rfc3987

@@

The feature generation strategy employed was derived from a distilled
portion of the approach introduced by Paulheim
and F\"urnkranz\cite{paulheim2012unsupervised}.

@@

For each approach, hierarchical clustering was applied repeatedly
until the next merge would produce a cluster with cohesion below 0.5.
This is reasonably arbitrary as each technique will have different
concepts of cohesion, but it provided a strong basis on which to
evaluate each approach on whether its cohesion meaningfully predicts
whether a human would agree that cluster contains related items.

### 2016-05-06 report/chapters/05-analysis.tex
First pass of chapter 6 (minus survey results)
Probably done with evaluation
Spell check

\chapter{Results and Analysis}

@@

\subsection{Few, Large Clusters}

@@

\subsubsection{Smallest Cluster}

@@

Again, there is potential to call out a real benefit in the
combination of in-page semantics for this ``hard'' categorical
data (i.e. the page's content is of type ``Radio Episode'') with
entity extraction for a looser, schemaless vocabulary of words that
more qualitatively describe the topics covered in the content.

@@

The result of this bug or unexpected behaviour is that variants
of the data pipeline that use deferencing as an extraction method will
have this propery for any page that does not use Microdata simply
because of the choice of RDF parsing library. There appears to be
enough mix of BBC content pages that do and do not use Microdata such
that this feature passed the feature selection filter that should
have removed any feature with the same value across the whole corpus.

@@

The fifth most common feature for this cluster is genuinely something
informative about the content in the page -- it appears to be a meta
tag informing of a title to use for the page on iOS devices. This is
again likely to be an artefact of how the BBC Sport section of the
BBC website is developed with requirements relating to iOS devices,
but it also -- perhaps inadvertantly -- tells us something semantic
about the page in that it is part of BBC Sport.

This may not be groundbreaking insight as there are clearly more
definitive ways to distinguish BBC Sport content (e.g. all the URLs
paths start with the word ``sport''), but it starts to showcase a
potential advantage of unsupervised learning on semantics that it
can use subtle clues based on how the pages are constructed to
determine something about them -- if this is deemed useful, that is.

It is also a showcase of how an unsupervised data mining process can
be said to have ``learned'' that these are all BBC Sport articles
without having to be instructed through bespoke business rules. This
hints at some need for further research as to whether enterprises
can truly adopt semantics and data mining to derice business rules
that survive organisational and systems changes due to being less
brittle than bespoke enterprise integration software based on static
business rules (i.e. rules that are true today but need updating when
the business context changes or risk breaking).

@@

\subsection{Impact of Noise}

@@

Thus it can be concluded that the mere existence of noise is not
enough to fault a particular configuration of our semantic data mining
system, but there is a need to answer the question as to whether the
noise is enough to overwhelm and confuse any machine learning
attempts. The question we look to answer in this research is which
of the variants of this experiemental system are more or less
susceptible to noise and errors and recommend how we might research
overcoming any false positives that do arise.

@@

Some of the analysis in section~\ref{sec:anal-comparison} touched on
some of the side effects of semantics being tied to \emph{how} a page
was built rather than \emph{what} the page is about. It was also
shown semantics are being included due to  pressures from social media
organisations for content
providers to describe summaries of their content for better display
and discovery. Based on this and other observations in the clusters
produced, clustering based on deferencing URLs and reading their
embedded semantics has the following advantages:

@@

Exploratory analysis does not highlight any major strengths from
hyperlink exraction alone. Common properties centre almost entirely
around links to common pages such as FAQs, help pages, etc. due to the
lack of constraints in the system implemented to narrow the extraction
to ``interesting'' links from within the content itself.

@@

\subsection{Enrichment by Dereference}

@@

Enrichment via dereference was less dramatic for in-page semantics
themselves extracted via dereference. Whilst not called out
specifically in section~\ref{sec:anal-comparison}, a general trend
was for those semantics exclusively to contain literals as values.

@@

\section{Recommendations for Production Use}

@@

Haas et al.\cite{haas2011enhanced} provided evidence in 2011 that
fewer than four percent of pages retrieved via Yahoo US search
contained RDFa markup. In a media organisastion that has no culture
of technical employees with an interest in the semantic web or
linked data, there may be no pages with semantic metadata purposely
added. However, if we embrace meta tags intended for social media
websites, exploratory analysis of BBC metadata in this research
suggests a ubiquity of such semantics driven entirely without the
academic push behind the Semantic Web and Linked Data.

We can therefore see social media annotations as compromise between
benefits of semantic markup and the pragmatic concerns that authors
will not add hidden metadata without clear, immediate benefits. It is
hoped that the reults of this research show that there are some
baseline benefits to an initial round of data mining on those
semantics alone and gaps and failures can create the incentives for
web page authors and engineers to improve their semantics and see
immediate benefits (e.e. their pages get promoted more readily in
pan-site signposting such as sets of ``related content'' suggestions).

@@

For example, programme
information and catch-up pages are excellent at describing themselves
as being TV or radio programmes and BBC News has the early stages of
pages that aggregate News over a given topic, but there is no
cross-linked data where concepts are covered both in a news article
and in a programme. This will emerge in organisations where distinct
teams and divisions work on very distinct parts of their output, so
any data mining concerned with the whole corpus needs to highlight
issues from lack of cross-linking as much as possible, particuarly
if that data mining is driving a real website feature that will see
immediate improvement if such cross-linking is implemented.

>>>>

\chapter{Results and Analysis}
\label{chp:analysis}

@@

\subsection{Few, Large Clusters}
\label{sec:few-large}

@@

\subsubsection{Smallest Cluster}
\label{sec:smallest-cluster}

@@

Again, there is potential to call out a real benefit in the
combination of in-page semantics for this ``hard'' categorical
data (i.e. the page's content is of type ``Radio Episode'') with
entity extraction for a looser, schema-less vocabulary of words that
more qualitatively describe the topics covered in the content.

@@

The result of this bug or unexpected behaviour is that variants
of the data pipeline that use dereferencing as an extraction method will
have this property for any page that does not use Microdata simply
because of the choice of RDF parsing library. There appears to be
enough mix of BBC content pages that do and do not use Microdata such
that this feature passed the feature selection filter that should
have removed any feature with the same value across the whole corpus.

@@

The fifth most common feature for this cluster is genuinely something
informative about the content in the page -- it appears to be a meta
tag informing of a title to use for the page on iOS devices. This is
again likely to be an artefact of how the BBC Sport section of the
BBC website is developed with requirements relating to iOS devices,
but it also -- perhaps inadvertently -- tells us something semantic
about the page in that it is part of BBC Sport.

This may not be ground-breaking insight as there are clearly more
definitive ways to distinguish BBC Sport content (e.g. all the URLs
paths start with the word ``sport''), but it starts to showcase a
potential advantage of unsupervised learning on semantics that it
can use subtle clues based on how the pages are constructed to
determine something about them -- if this is deemed useful, that is.

It is also a showcase of how an unsupervised data mining process can
be said to have ``learned'' that these are all BBC Sport articles
without having to be instructed through bespoke business rules. This
hints at some need for further research as to whether enterprises
can truly adopt semantics and data mining to derive business rules
that survive organisational and systems changes due to being less
brittle than bespoke enterprise integration software based on static
business rules (i.e. rules that are true today but need updating when
the business context changes or risk breaking).

@@

\subsection{Impact of Noise}
\label{sec:impact-of-noise}

@@

Thus it can be concluded that the mere existence of noise is not
enough to fault a particular configuration of our semantic data mining
system, but there is a need to answer the question as to whether the
noise is enough to overwhelm and confuse any machine learning
attempts. The question we look to answer in this research is which
of the variants of this experimental system are more or less
susceptible to noise and errors and recommend how we might research
overcoming any false positives that do arise.

@@

Some of the analysis in section~\ref{sec:anal-comparison} touched on
some of the side effects of semantics being tied to \emph{how} a page
was built rather than \emph{what} the page is about. It was also
shown semantics are being included due to  pressures from social media
organisations for content
providers to describe summaries of their content for better display
and discovery. Based on this and other observations in the clusters
produced, clustering based on dereferencing URLs and reading their
embedded semantics has the following advantages:

@@

Exploratory analysis does not highlight any major strengths from
hyperlink extraction alone. Common properties centre almost entirely
around links to common pages such as FAQs, help pages, etc. due to the
lack of constraints in the system implemented to narrow the extraction
to ``interesting'' links from within the content itself.

@@

\subsection{Enrichment by Dereference}
\label{sec:anal-enrichment}

@@

Enrichment via dereference was less dramatic for in-page semantics
themselves extracted via dereference. While not called out
specifically in section~\ref{sec:anal-comparison}, a general trend
was for those semantics exclusively to contain literals as values.

@@

\section{Recommendations for Production Use}
\label{sec:production-recommendations}

@@

Haas et al.\cite{haas2011enhanced} provided evidence in 2011 that
fewer than four percent of pages retrieved via Yahoo US search
contained RDFa markup. In a media organisation that has no culture
of technical employees with an interest in the semantic web or
linked data, there may be no pages with semantic metadata purposely
added. However, if we embrace meta tags intended for social media
websites, exploratory analysis of BBC metadata in this research
suggests a ubiquity of such semantics driven entirely without the
academic push behind the Semantic Web and Linked Data.

We can therefore see social media annotations as compromise between
benefits of semantic markup and the pragmatic concerns that authors
will not add hidden metadata without clear, immediate benefits. It is
hoped that the results of this research show that there are some
baseline benefits to an initial round of data mining on those
semantics alone and gaps and failures can create the incentives for
web page authors and engineers to improve their semantics and see
immediate benefits (e.e. their pages get promoted more readily in
pan-site signposting such as sets of ``related content'' suggestions).

@@

For example, programme
information and catch-up pages are excellent at describing themselves
as being TV or radio programmes and BBC News has the early stages of
pages that aggregate News over a given topic, but there is no
cross-linked data where concepts are covered both in a news article
and in a programme. This will emerge in organisations where distinct
teams and divisions work on very distinct parts of their output, so
any data mining concerned with the whole corpus needs to highlight
issues from lack of cross-linking as much as possible, particularly
if that data mining is driving a real website feature that will see
immediate improvement if such cross-linking is implemented.
